\section{Work Experience}

\resumeSubHeadingListStart

\resumeSubheading
{MAQ Software}
{Noida, India}
{\textbf{Software Engineer(Churn Analysis)}}{Dec 2021 - Present}
\vspace{-2.0mm}
\resumeItemListStart
\item {
            Initiated and directed the '\textbf{Churn Analysis}' project, addressing business challenges related to churn. In testing phase, demonstrating a \textbf{90\%\ accuracy} in predicting business churn—a valuable asset for clients.}
\item {
            Collaborated with design team to precisely convert Figma designs into visually captivating and user-friendly frontend code, resulting in a 20\%\ increase in user satisfaction and a 30\%\ reduction in user error rates.}
\item {
            Incorporated \textbf{React.js, Redux, Material UI} and a charting library to craft an intelligent and engaging frontend. Elevated user experience and data visualization, resulting in a \textbf{25\%\ improvement in user engagement}.}
\item {
            Implemented RESTful APIs in Flask for seamless frontend integration, \textbf{incorporating OpenAI API} to devise strategies for minimizing churn and identifying reasons for elevated business churn. Engineered API caching, optimized computations with useMemo and useCallback, achieving a \textbf{15\%\ reduction in page load time}.
      }

\resumeItemListEnd

\vspace{-8.0mm}

\resumeSubheading{}{}
{\textbf{Software Engineer(Examin library)}}{}
\vspace{-2.0mm}
\resumeItemListStart
\item {
            Reverse-engineered and debug an existing React.js extension to comprehend the workflow, subsequently modifying it for compatibility with different UI frameworks—Fluent UI, Material UI, and Bootstrap UI. This adaptation successfully covered 70\%\ of a client project, enabling the generation of comprehensive unit and rendered test cases.}
\item {
            Examin extension autonomously generated over 450 rendered test cases for React solutions, significantly enhancing the testing coverage and ensuring robust code quality.
      }

\resumeItemListEnd

% \vspace{-3.0mm} 
\vspace{-8.0mm}

\resumeSubheading{}{}
{\textbf{Associate Software Engineer}}{}
\vspace{-2.0mm}
\resumeItemListStart
\item {
            Led accessibility initiatives in the development team, ensuring each element met rigorous accessibility (a11y) standards by incorporating \textbf{semantic HTML tags and JavaScript library} in code. \textbf{Conducted thorough testing} to ensure compatibility across popular browsers (Chrome, Mozilla Firefox, Safari). }
\item {
            Executed a feature ticket by seamlessly replacing a deprecated tagging component with a new one, ensuring uninterrupted functionality and preserving \textbf{consistent performance} and \textbf{user experience}.}
\item {
            Conducted thorough testing on build size, comparing measurements before and after the removal of deprecated components using \textbf{Webpack}. This initiative contributed to \textbf{optimizing the application's performance} and overall efficiency.}
\item {
            \textbf{Implemented a thorough testing strategy} using \textbf{React.js and QUnit}, with diverse test cases for existing features and new components developed by me, achieving \textbf{90\%+\ code coverage}. Encompassing \textbf{unit, integration, and application (end-to-end) tests}, this approach ensured a robust and reliable codebase, significantly enhancing the \textbf{overall quality and stability} of the application.}

\resumeItemListEnd

\vspace{-3.0mm}

\resumeSubHeadingListEnd
\vspace{-5.5mm}
