\section{Personal Projects}

\resumeSubHeadingListStart

\resumeProject{\href{https://github.com/pesto-students/team1-manish-team1-manish}{{\underline{Car Bazaar}}}}
{Carbazaar: List and sell cars; buyers browse, make purchases. Vehicle marketplace.} %Project Name, Location Name
{}{}

\resumeItemListStart
\item {Designed and developed a \textbf{car listing} website with \textbf{seamless online} vehicle purchase capabilities for registered users.}
\item {Utilized \textbf{React.js} and \textbf{Redux} for a user-friendly and engaging experience on UI, used \textbf{Material UI} to develop Component.}
\item {Established a secure backend employing \textbf{Node.js}, \textbf{Express.js}, and \textbf{PostgreSQL} for data management. Integrated \textbf{Passport.js} for user authentication (Google, login password), along with \textbf{Razor Pay's} test mode payment gateway.}
\resumeItemListEnd

\resumeProject
{\href{https://github.com/SaurabhK05/Daily-news-app}{\underline{Daily News Application}}} %Project Name
{Built a new app for daily weather updates, providing users with daily weather forecasts conveniently.} %Project Name, Location Name
{}{}

\resumeItemListStart
\item {Leveraged \textbf{React.js}, \textbf{React Hooks}, and \textbf{Redux Toolkit} for efficient \textbf{global state management} in developing the application.}
% \item {Have used a open source API to get news information and rendered it on UI.
\item {Utilised an \textbf{open-source API (newsapi.org)} to fetch news and seamlessly integrated it into the user interface.}

\resumeItemListEnd

\resumeSubHeadingListEnd
